Memristor-based recurrent modules for neural computing

### 2023-10-31 paper/conclusion.tex
Fixed one mistake

With a simple input sequence, such as sequence 5 (\cref{graph:celegansAnalog1}), the resulting predictions are quite good and on par with what is expected. The predictions are a bit late and it is not clear what is causing this specific issue. A theory is that the memory cells deteriorate its stored value by a very small amount every time step, thus the stored value is affectd a lot after a large amount of time steps.

>>>>

With a simple input sequence, such as sequence 5 (\cref{graph:celegansAnalog1}), the resulting predictions are quite good and on par with what is expected. The predictions are a bit late and it is not clear what is causing this specific issue. A theory is that the memory cells deteriorate its stored value by a very small amount every time step, thus the stored value is affected a lot after a large amount of time steps.
